
% TODO bibtex

\section{Further Reading}
[BALE~2014] Bale, A (2014): BitVote, Vote With Your Live, Whitepaper, 11 June~2014, Louisville, Kentucky, United States of America.\par
[BORGSTRUP~2014] Borgstrup, J (2014): Private, Trustless And Decentralized Message Consensus And Voting Schemes, Master's Thesis, 23~November~2014, University of Copenhagen, Denmark.\par
[BUTERIN~2014] Buterin, V (2014): A Next-Generation Smart Contract And Decentralized Application Platform, Ethereum Whitepaper, 11~January~2014, Ethereum Project: http://vbuterin.com/ethereum.html\par
[BUTERIN~2015] Buterin, V (2015): Understanding Serenity, Part I: Abstraction, Ethereum Blog, 24~December~2015, Canada.\par
[COYNE~2015] Cyone, C (2015): New Voting System Proposed For~2016 SGA Elections, The Daily Athenaeum, 19~November~2015, Morgantown, West Virginia, United States of America.\par
[DEMOCRACYOS~2015A] Anonymous (2015): Blockchain support for DemocracyOS, DemocracyOS Blog, 19~March~2015, Buenos Aires, Argentina.\par
[DEMOCRACYOS~2015B] Anonymous (2015): Why blockchain support for DemocracyOS, DemocracyOS Blog, 24 June~2015, Buenos Aires, Argentina.\par
[ELVIRA~2013] Elvira, ER (2013): A Bitcoin Based, Completely Distributed Voting System, 28~November~2013, Agora Voting Blog, Madrid, Spain.\par
[ÉPIÉ~et~al.~2015] Épié, C; Loubet, N (2015): Blockchain and Beyond, Version 1.0, 3~December~2015, Cellabz, Paris, France.\par
[ERFURT~2015] Erfurt, D (2015): Ein dezentrales Transitionssystem zur Manipulation von geteilten Wörtern einer regulären Sprache, Bachelor's Thesis, 25 June 2015, Humboldt University, Berlin, Germany.\par
[ERFURT~2016] Erfurt, D (2016): Efficient Decentral Governance of Structured Data, Whitepaper, 21~March~2016, Berlin, Germany: http://memhub.io/whitepaper\par
[ERNEST~2014] Ernest, AK (2014): The Key To Unlocking The Black Box: Why The World Needs A Transparent Voting DAC, 4~July~2014, Follow My Vote, Blacksburg, Virginia, United States of America.\par
[ERNEST~2016] Ernest, AK (2016): Follow My Vote, 26~January~2016, In: Report On Secure Voting, A Guide To Secure \#onlinevoting In Elections, Webroots Democracy, United Kingdom.\par
[HOURT~2015A] Hourt, N (2015): End to End Verified Voting On A Blockchain, 3~September~2015, Follow My Vote, Youtube: https://youtu.be/EE2mWoio7po\par
[HOURT~2015B] Hourt, N (2015): How Our Voter Registration Process Works, 16~December~2015, Follow My Vote, Youtube: https://youtu.be/GcAz9mZW1\_c\par
[JOHNSTON~et~al.~2013] Johnston, DA; Yilmas, SO; Kandah, J; Bentenitis, N; Hashemi, F; Gross, R; Wilkinson S; Mason, S (2013): The Generalized Theory Of Decentralized Applications, DApps,~20~November~2013, DAppsFund, Austin, Texas, United States of America.\par
[KAYE~2014] Kaye, M (2014): A First Attempt To Describe The Neutral Voting Bloc, 2~July~2014, VoteFlux, Sydney, Australia.\par
[KAYE~2016] Kaye, M (2016): Public VoteFlux Slack Channel Archive (\#general), 12~March~2016, VoteFlux, Sydney, Australia.\par
[KONASHEVYCH~2016] Konashevych, O (2016): What Are We Doing, 25~February~2016, E-Vox.org, Kiev, Ukraine.\par
[LARIMER~2016] Larimer, D (2016): How To Build A Decentralized Application Without Fees, 10~February~2016, Bitshares, Blacksburg, Virginia, United States of America.\par
[LEVEL~2014] Level, C (2014): VoteCoin, A fair, transparent, practical solution to fix modern voting, VoteCoin Blog, 9~December~2014, United States of America.\par
[MANCINI~2015] Mancini, P (2015): Blockchain Support For Open Source Platform Democracyos, Newschallenge, 17~March~2015, San Francisco, California, United States of America.\par
[MANCINI~et~al.~2015] Mancini, P; Siri, S (2015): Democracy Earth, Power In Your Hands, A Decentralized Global Commons Of Peers, San Francisco, California, United States of America.\par
[MARGOT-DUCLOT~2015] Margot-Duclot, L (2015): Nemos, Whitepaper, 2015, Paris, France.
[MONEGRO~2014] Monegro, J (2014): The Blockchain Application Stack, 25~November~2014, Union Square Ventures, New York, United States of America.\par
[NAKAMOTO~2008] Nakamoto, S (2008): Bitcoin, A Peer-to-Peer Electronic Cash System, Bitcoin Whitepaper, 31~October~2008, Metzdowd Cryptography Mailing List: https://bitcoin.org/bitcoin.pdf\par
[NOIZAT~2014] Noizat, P (2014): Blockchain Electronic Vote, Unchain.Voting Whitepaper, 30~July~2014, Paymium, Paris, France.\par
[ROCKWELL~2014] Rockcoons \enquote{Rockwell}, M (2014): BitCongress, Whitepaper, Blockchain Based Voting System, 16~October~2014, Bitcoin Kinetics, Beaverton, Oregon, United States of America.\par
[SCHIENER~2015A] Schiener, D (2015): Public Votes, Ethereum-based Voting Application, 28~October~2015, South Tyrol, Italy.\par
[SCHIENER~2015B] Schiener, D (2015): Voting on the Ethereum Blockchain, An Analysis, 7~November~2015, South Tyrol, Italy.\par
[SCOTT~2016] Scott, B (2016): How Can Cryptocurrency And Blockchain Technology Play A Role In Building Social And Solidarity Finance, Working Paper~2016-1, 25~February~2016, United Nations Research Institute for Social Development, Geneva, Switzerland.\par
[VARSHNEYA~et~al.~2015] Varshneye, AJ; Poudel, S; Vyas, X (2015): Blockchain Voting, CS4501 Cryptocurrency Cabal, 7~December~2015, University of Virginia, United States of America.\par
[WOOD~2014] Wood, G (2014): Ethereum, A Secure Decentralised Generalised Transaction Ledger, Ethereum Yellowpaper, 6~April~2014, Ethereum Project: http://gavwood.com/paper.pdf

% @TODO refs nemos io
